
\documentclass{resume} % Use the custom resume.cls style 
\usepackage[dvipsnames]{xcolor}
\usepackage{url}
\usepackage[left=0.4 in,top=0.3 in,right=0.4 in,bottom=0.3in]{geometry}
\usepackage{hyperref} 

% Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Mingxuan Liu} % Your name 
\address{Center of Biomedical Imaging Research (CBIR), Tsinghua University, Beijing, P.R. China} % Your address 
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional) 
\address{+86 13517753399 \\ arktisx@foxmail.com \\ \href{https://arktis2022.github.io/}{Personal Homepage} \\ \href{https://scholar.google.com.hk/citations?hl=zh-CN&user=8VyGtD0AAAAJ}{Google Scholar}} % Your phone number and email

\definecolor{TsinghuaPurple}{cmyk}{0.58,0.90,0,0}
\renewenvironment{rSection}[1]{
\sectionskip
\textcolor{TsinghuaPurple}{\MakeUppercase{#1}}
\sectionlineskip
\hrule
\begin{list}{}{
%\setlength{\leftmargin}{1.5em}
\setlength{\leftmargin}{0em}
}
\item[]
}{
\end{list}
}


\begin{document}  

\begin{rSection}{Education}

{\bf PhD Student, School of Biomedical Engineering, Tsinghua University, China} \hfill {2024.09 - Now}
\\ 
    Advisor: Prof. Qiyuan Tian
\\
{\bf BEng Student, School of Biomedical Engineering, Tsinghua University, China} \hfill {2021.09 - 2024.08}
\\ 
{\bf BEng Student, Department of Chemical Engineering, Tsinghua University, China} \hfill {2019.09 - 2021.08}

\end{rSection}


\begin{rSection}{Awards and Honors}
\begin{itemize}
    \item ISMRM Workshop Trainee Stipend Award (Awarded: \$1500) \hfill{2026}
    \item ISMRM Educational Stipend Award \hfill{2026}
    \item Tsinghua CBIR Annual Retreat Oral Session 2nd Place \hfill{2026}
    \item BEIHAI Summit Second Prize of Oral Presentation \hfill{2025}
    \item National Scholarship, Ministry of Education, P.R. China \hfill{2025}
    \item MICCAI autoPET IV Challenge 1st Place Winner \hfill{2025}
    \item MICCAI VLM3D Challenge 2nd Place Winner \hfill{2025}
    \item OHBM Merit Award  (Awarded: \$850, Top 1.6\%) \hfill{2025}
    \item ISMRM Educational Stipend Award \hfill{2025}
    \item National Scholarship, Ministry of Education, P.R. China \hfill{2024}
    \item First Prize at National Biomedical Engineering Innovation Design Competition for College Students \hfill{2024}
    \item Outstanding Graduates of Beijing, Beijing Municipal Administration Committee \hfill{2024}
    \item Outstanding Graduates of Tsinghua University \hfill{2024}
    \item ISMRM Magna Cum Laude Merit Award (Top 15\%) \hfill{2024}
    \item ISMRM Educational Stipend Award \hfill{2024}
    \item IEEE ICCBD+AI Best Paper Award \hfill{2024}
    \item Singapore Al Health Summit Poster Competition 3rd Place Winner (Awarded: \$3000) \hfill{2023}
    \item National Scholarship, Ministry of Education, P.R. China \hfill{2023}
    \item Scholarship for Academic Excellence, Tsinghua University \hfill{2022}
    \item Scholarship for Science and Technology Innovation Excellence, Tsinghua University \hfill{2022}
    \item Second Prize for Outstanding Projects of the Students Research Training Program, Tsinghua University \hfill{2022}
    \item Scholarship for Academic Excellence, Tsinghua University \hfill{2020}
\end{itemize}
\end{rSection}

%   Research Publications 
%--------------------------------------------------------------------------------------
\begin{rSection}{Selected Publication} %\itemsep -3pt  
\# co-first author $|$ * corresponding author

\textbf{JOURNAL PAPERS}

\begin{itemize}
    \item \textbf{Liu M\#}, Liao Y\#, Li H, Zhu J, Yang H, Hao Y, Qu H*, Tian Q*. \textit{Quality-label-free Fetal Brain MRI Quality Control Based on Image Orientation Recognition Uncertainty.} Medical Image Analysis, 2026. DOI: \url{https://doi.org/10.1016/j.media.2026.103994}

    \item \textbf{Liu M\#}, Tang J\#, Li H, Yong C, Qi J, Li S, Wang K, Gan J, Wang Y*,  Chen H*.  \textit{Spiking-PhysFormer: Camera-Based Remote Photoplethysmography with Parallel Spike-driven Transformer.} Neural Networks, 2025. DOI: \url{https://doi.org/10.1016/j.neunet.2025.107128}
 
    \item \textbf{Liu M}, Jiao Y, Lu J, Chen H*. \textit{Anomaly Detection for Medical Images Using Teacher–Student Model with Skip Connections and Multiscale Anomaly Consistency.} IEEE Transactions on Instrumentation and Measurement, 2024. DOI: \url{https://doi.org/10.1109/TIM.2024.3406792} 

    \item Wu C\#, Chen Y\#, Du Y, Zong J, Dong J, \textbf{Liu M}, Qin F*, Peng Y, Fan J, Wang C. \textit{Towards practical Alzheimer’s Disease diagnosis: A lightweight and interpretable spiking neural model.} Biomedical Signal Processing and Control, 2026, 117:109595. DOI: \url{https://doi.org/10.1016/j.bspc.2026.109595}

    \item Zheng J, Li Z, Zhong W, Wang Z, Li Z, Yang H, \textbf{Liu M}, Cao X, Liao C, Salat DH, Huang SY, Tian Q. \textit{Effects of diffusion MRI spatial resolution on human brain short-range association fiber reconstruction and structural connectivity estimation.} Imaging Neuroscience, 2025. DOI: \url{https://doi.org/10.1162/IMAG.a.1089}
\end{itemize}

\textbf{SELECTED CONFERENCE PAPERS}

\begin{itemize}
    \item \textbf{Liu M\#}, Li Y\#, Zhu J\#, Yang H, Huang Y, Li H, Chen Y, Bai X, Liao Y, Qu H, Tian Q*. \textit{FetalExtract-LLM: Structured Information Extraction in Free-Text Fetal MRI Reports Based on Privacy-Ensuring Open-weights Large Language Models.} MICCAI Workshop on Perinatal, Preterm and Paediatric Image Analysis (PIPPI), 2025. (Oral) Link: \url{https://doi.org/10.1007/978-3-032-05997-0_11}

    \item Bai X\#, \textbf{Liu M\#}, Chen Y, Yang H, Tian Q*. \textit{Chest-OMDL: Organ-specific Multidisease Detection and Localization in Chest Computed Tomography using Weakly Supervised Deep Learning from Free-text Radiology Report.} Medical Imaging with Deep Learning (MIDL), 2025. (Poster) Link: \url{https://openreview.net/forum?id=ns6nq592HX}

    \item Li H\#, \textbf{Liu M\#}, Bai X, Liao Y, Zheng J, Yang H, Li Z, Qu H, Tian Q*. \textit{FetalCSR: Multi-input Attention Fusion Network for Neural ODE-based Fetal Cortical Surface Reconstruction.} ICLR Workshop on AI for Children (AI4CHL), 2025. (Oral) Link: \url{https://openreview.net/forum?id=Ra0xioC3He}

    \item Lin X\#, \textbf{Liu M\#}, Liu K, Chen H. \textit{Spike-SLR: An Energy-efficient Parallel Spiking Transformer for Event-based Sign Language Recognition.} The British Machine Vision Conference (BMVC), 2024. (Poster) Link: \url{https://papers.bmvc2024.org/0493.pdf} 

    \item Li S\#, \textbf{Liu M\#}, Zhang Y, Chen S, Li H, Chen H, Dou Z. \textit{SAM-Deblur: Let Segment Anything Boost Image Deblurring.} IEEE International Conference on Acoustics, Speech and Signal Processing (ICASSP), 2024. (Poster) Link: \url{https://doi.org/10.1109/ICASSP48485.2024.10445844}

    \item \textbf{Liu M\#}, Gan J\#, Wen R\#, Li T, Chen Y, Chen H*. \textit{Spiking-Diffusion: Vector Quantized Discrete Diffusion Model with Spiking Neural Networks.} International Conference on Computer, Big Data and Artificial Intelligence (ICCBD+AI), 2024. (Best paper award) Link: \url{https://doi.org/10.1109/ICCBD-AI65562.2024.00110}

    \item \textbf{Liu M}, Jiao Y, Chen H*. \textit{Skip-ST: Anomaly Detection for Medical Images Using Student-Teacher Network with Skip Connections.} IEEE International Symposium on Circuits and Systems (ISCAS), 2023. (Oral) Link: \url{https://doi.org/10.1109/ISCAS46773.2023.10181639}

    \item \textbf{Liu M}, Jiao Y, Gu H, Lu J, Chen H, \textit{Data Augmentation Using Image-to-image Translation for Tongue Coating Thickness Classification with Imbalanced Data.} IEEE Biomedical Circuits and Systems Conference (BioCAS), 2022. (Oral) Link: \url{https://doi.org/10.1109/BioCAS54905.2022.9948645}
\end{itemize}

\textbf{SELECTED CONFERENCE ABSTRACTS}

\begin{itemize}
\item \textbf{Liu M}, Li H, Yang H, Liao Y, Zhu J, Zheng J, Hao Y, Li Z, Li Z, Wang Z, Li Y, Huang J, Ning G, Qu H, Tian Q*. \textit{Cortical Brain in Utero Growth Among Fetuses with Germinal Matrix and Intraventricular Hemorrhage (GMH-IVH).} ISMRM \& ISMRT Annual Meeting \& Exhibition, 2026. (Digital Poster) Link: \url{http://echo.ismrm.org/abstracts/view/786064de-0ae1-469e-a161-a8d03618044b}

\item \textbf{Liu M}, Hao Y, Liao Y, Li H, Zhu J, Yang H, Chen Y, Bai X, Qu H, Tian Q*. \textit{Quality-Label-Free Stack-Level Quality Control Improves Fetal Brain Slice-to-Volume Reconstruction.} ISMRM Workshop on Unlocking the Potential of Prenatal MRI, 2026. (Traditional Poster) Link: \url{https://echo.ismrm.org/abstracts/view/fedc0bc4-ed95-4361-a9c6-0ce061f610b3}

\item \textbf{Liu M}, Li H, Li Z, Yang H, Zheng J, Qu H, Tian Q*. \textit{Unsupervised Fetal Brain MRI Quality Assessment based on Orientation Prediction Uncertainty.} OHBM Annual Meeting, 2025. (Poster) [OHBM Merit Award, Top 1.6\%] Link: \url{https://hal.science/hal-04974115}

\item \textbf{Liu M}, Liao Y, Zhu J, Li H, Yang H, Zheng J, Li ZH, Li ZY, Qu H, Tian Q*. \textit{FreeHemoSeg: Label-Free Deep Learning Framework for Automated Segmentation of Fetal Brain Germinal Matrix and Intraventricular Hemorrhage.} The Annual Meeting of ISMRM, 2025. (Digital Poster) Link: \url{https://archive.ismrm.org/2025/3790.html}

\item \textbf{Liu M}, Li Y, Zhu J, Yang H, Huang Y, Li H, Chen Y, Bai X, Liao Y, Qu H, Tian Q*. \textit{From Free Text to Usable Labels: Privacy-Ensuring Open-weights LLM-Enhanced Clinical Report Extraction for Fetal MRI.} Beijing-Tsinghua Health AI Summit (BEIHAI), 2025. (Oral) [Second Prize of Oral Presentation] Link: \url{https://hal.science/hal-05330462}

\item \textbf{Liu M}, Li H, Zhu J, Zheng J, Yang H, Li Z, Li Z, Tian Q*. \textit{Detecting Fetal Germinal Matrix and Intraventricular Hemorrhage in Brain MRI Using Label-free Deep Learning.} The Annual Meeting of the Radiological Society of North America (RSNA), 2024. (Oral) Link: \url{https://hal.science/hal-04961196}

\item \textbf{Liu M}, Li H, Li Z, Yang H, Zheng J, Zhang X, Tian Q*. \textit{Image Quality Assessment using an Orientation Recognition Network for Fetal MRI.} The Annual Meeting of ISMRM, 2024. (Oral Power Pitch) [Magna Cum Laude Merit Award, Top 15\%] Link: \url{https://archive.ismrm.org/2024/0726.html}

\item \textbf{Liu M}, Li H, Liao Y, Qu H, Tian Q*. \textit{Label-free Image Quality Assessment of Fetal Brain MRI with Unsupervised Deep Learning.} Singapore AI Health Summit, 2023. (Poster Competition 3rd Place Winner, Top 3\%) Link: \url{https://hal.science/hal-04961169}
\end{itemize}

\textbf{SELECTED MANUSCRIPTS UNDER REVIEW}

\begin{itemize}
    \item \textbf{Liu M\#}, Hao Y\#, Liao Y\#, Zhu J, Li H, Yang H, Chen Y, Li Y, Anmahapong K, Li Z, Zheng J, Kang M, Song Y, Lai H, Zhou X, Ning G, Qu H*, Tian Q*. \textit{Annotation-free Deep Learning for Automated Detection and Segmentation of Fetal Germinal Matrix-Intraventricular Hemorrhage in Brain MRI.} The Lancet Medical Imaging \& Theranostics. (Under Review)

    \item \textbf{Liu M\#}, Bai X\#, Zhang M, Chen Y, Yang H, Wang Z, Luo Y, Zhou Y, Han X*, Tian Q. \textit{Preoperative CTA-based Deep Learning Model for Predicting AKI after TEVAR in Type B Aortic Dissection.} Radiology: Artificial Intelligence. (Submitting)

    \item Hao Y\#, \textbf{Liu M\#}, Zhu J\#, Yang H, Li H, Ning G, Liao Y, Qu H*, Tian Q*. \textit{PANDA: Patch-based Unsupervised Deep Learning for Brain Anomaly Detection via Age Prediction in Fetal MRI.} Imaging Neuroscience. (Under Review)

    \item Zong J\#, Chen Y\#, \textbf{Liu M\#}, Du Y, Wu C, Wu B, Zhou G, Qin F*. \textit{MUIT-TTA: Annotation-Free Intracranial Hemorrhage Segmentation via Pseudo-Anomaly Synthesis and Test-Time Adaptation.} Pattern Recognition. (Under Review)

    \item Hao Y\#, Luo Y\#, \textbf{Liu M\#}, Yang H, Hu X, Zhu J, Anmahapong K, Li Y, Li Z, Chen Y, Sun N, Hu R, Kang M, Song Y, Lai H, Zhou X, Ning G, Liao Y, Qu H*, Tian Q*. \textit{FetMRIE: Fetal Brain MRI Image Enhancement without Clean Reference.} Medical Image Analysis. (Submitting)

    \item Zhang Y\#, \textbf{Liu M\#}, Chen Y\#, Wu Y*, Zhang L, Guo M, Yan Y, Wei R, Cui Z, Luo P, Chen F, Yang B, Han Y, Liu X, Tian Q*. \textit{Multi-center Validation of Machine Learning Models for Predicting Myopia Progression across School-based Screening and Optical Intervention Settings in Chinese Children and Adolescents.} Advanced Intelligent Discovery. (Under Review)
    
    \item Yang H\#, Liao Y\#, \textbf{Liu M}, Zhu J, Li H, Jia F, Li Z, Zhang M, Zheng J, Wang Z, Zhang J, Chen Y, Li Y, Luo L, Liu J, Lai H, Zhou X, Kang M, Song Y, Ning G, Li Z, Zhang X, Qu H*, Tian Q*. \textit{3D Fetal Brain Morphometry from Single Thick-slice MRI Stacks Using Deep Learning Super-Resolution.} Nature Biomedical Engineering. (Under Review)

    \item Li H\#, \textbf{Liu M\#}, Varadarajan D, Hu Z, Tian Q*, Polimeni JR*. \textit{XSurfer: Reconstructing Surface Meshes of Cerebral and Cerebellar Cortex from Diverse MRI Data Using Untrained Neural Networks.} European Conference on Computer Vision (ECCV). (Under Review)
    \item Zhang X\#, \textbf{Liu M\#}, Chen Y, Zhu J, Anmahapong K, Huang Y, Zhang Y, Yang H, Liao Y, Ning G, Qu H, Tian Q*. \textit{ASTAR: Automated Induction of Standardized Medical Radiology Reporting Templates from Large-Scale Clinical Free-Text Corpora.} International Conference on Medical Image Computing and Computer Assisted Intervention (MICCAI). (Under Review)
    \item Hu X\#, \textbf{Liu M\#}, Yang H\#, Zhu J, Li Y, Chen Y, Li H, Li Z, Hao Y, Li Z, Zhang Y, Ning G, Liao Y, Qu H, Tian Q*. \textit{INFANiTE: Implicit Neural Representation for High-Resolution Fetal Brain Spatio-Temporal Atlas Learning from Clinical Thick-Slice MRI.} International Conference on Medical Image Computing and Computer Assisted Intervention (MICCAI). (Under Review)
    \item Li Y\#, \textbf{Liu M\#}, Chang L\#, Yang H, Anmahapong K, Wang Z, Hu X, Hao Y, Li H, Chen Y, Li X, Jia F, Liao Y, Qu H, Tian Q*. \textit{Maximizing Domain Generalization in Automated Fetal Brain Biometry.} International Conference on Medical Image Computing and Computer Assisted Intervention (MICCAI). (Under Review)
    
    \item Li Z\#, Xu Y\#, Zhang L, Han T, Yang X, Wang Y, \textbf{Liu M}, Xin S, Liu L, Liao H*, Ning G*. \textit{Democratizing Expert-Level Liver Sonography through an Autonomous Lightweight Ultrasound Robot.} Nature Biomedical Engineering. (Major Revision)

    \item Zhang M\#, Yang H\#, Xiao J, Liu W, Yin T, He Y, Zheng J, Li Z, \textbf{Liu M}, Liu W, Liao C, Bilgic B, Polimeni JR, Huang SY, Liao Y, Li Z*, Qu H*, Tian Q*. \textit{SRNR: Deep Learning-based MRI Super-Resolution Using Noisy High-Resolution Reference Data.} Imaging Neuroscience. (Major Revision)
    
    \item Chen Y\#, Zheng J\#, Wang Y\#, Wu B, Li L, \textbf{Liu M}, Xu L, Wu Y, Liu C, Guo L, Yang H, Bai X, Qin F, Liao Q, Gu Y, Zhao G, Ma L, Pan K, Guo J, Zhou Y, Sun H*, Tian Q*. \textit{A Chinese Vision-Language Large Model for Emergency 3D Brain CT Interpretation.} npj Digital Medicine. (Minor Revision)
    
    \item Chen Y\#, Li Z\#, Wang Y, Li Y, Zheng J, Yang H, \textbf{Liu M}, Cukur T, Li Z, Tian Q*. \textit{MicroKAN: Mapping Human Brain Microstructure Using Diffusion MRI and Convolutional Kolmogorov--Arnold Network.} NeuroImage. (Major Revision)

\end{itemize}

\end{rSection}

\begin{rSection}{Academic Service} 
\begin{itemize}
    \item Conference Co-organizer: \href{http://www.ocsmrm.org/}{OCSMRM 2024}, \href{https://www.medcircle.cn/meeting/index/2025bs}{BEIHAI Summit 2025}, MICS 2026.
    \item Journal Reviewer: Applied Intelligence, Biomedical Signal Processing and Control, Engineering Applications of Artificial Intelligence, IEEE Transactions on Cognitive and Developmental Systems, IEEE Transactions on Human-Machine Systems, Neural Networks, Neurocomputing, Pattern Recognition.
    \item Conference Reviewer: AAAI, ACM MM, ACM MobileHCI, BMVC, CHIL, ICASSP, ICME, IJCNN, ISBI, ISMRM, MICCAI, MIDL, NeurIPS, AAAI/ICLR/ICML Workshop.

    \item Teaching Assistant: 
    \begin{itemize}
        \item Medical Image Processing (Undergraduate Course, 3 Units), School of Biomedical Engineering, Tsinghua University, 2024/2025.
        \item TIC3/4: Technological Innovation and Challenges 3/4, Weixian College, Tsinghua University, 2024/2025/2026.
    \end{itemize}
\end{itemize}
\end{rSection}
%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Invited Talks} 
\begin{itemize}
    \item 2026 ISMRM Workshop on Unlocking the Potential of Prenatal MRI \href{https://drive.google.com/file/d/198B0ugGdbdbMRqvSAq84R0zBUxSjRdHD/view?usp=sharing}{Slides}
    \item 2025 The 2nd Graduate Academic Forum (School of Biomedical Engineering, Tsinghua University) \href{https://drive.google.com/file/d/1a4Ep2LnBZ9o9DM7xXGL481cpLCWPvhAr/view?usp=sharing}{Slides}
    \item 2025 Beijing-Tsinghua Health AI Summit (To Rupa Sarkar, Editor-in-Chief of The Lancet Digital Health) \href{https://drive.google.com/file/d/1KZ3uCLT2vhe4t_zkzr2JK20RqKMVKza-/view?usp=sharing}{Slides}
    \item 2025 MICCAI Workshop on Perinatal, Preterm and Paediatric Image Analysis (PIPPI) \href{https://drive.google.com/file/d/1TqsbKEgtEncdmPOLj9SEu5VSDl93JYhE/view?usp=sharing}{Slides}
    \item 2024 Annual Meeting of Radiological Society of North America (RSNA) \href{https://drive.google.com/file/d/1hlm_mN9PHqESGGoi8Leza0BJjlYYiEXW/view?usp=sharing}{Slides}
    \item 2024 ISMRM \& ISMRT Annual Meeting \& Exhibition (ISMRM) \href{https://drive.google.com/file/d/10SDrVys-hjzbKhKGVHmTuwDiKJMWc1bm/view?usp=sharing}{Slides}
    \item 2023 Singapore AI Health Summit \href{https://drive.google.com/file/d/1KyM7mMnvgtCK5bdyR1nTItZZwuh1rvxp/view?usp=sharing}{Slides}
    \item 2023 IEEE International Symposium on Circuits and Systems (ISCAS) \href{https://drive.google.com/file/d/17mfjEbcE8I3G1Xjeu2GkwPS5WB5TJruq/view?usp=sharing}{Slides}
    \item 2022 IEEE Biomedical Circuits and Systems Conference (BioCAS) \href{https://drive.google.com/file/d/1-6_6UtHRDhAlHtSXjJH1kXoZ6Si4hL_j/view?usp=sharing}{Slides}
\end{itemize}



\end{rSection}

\begin{rSection}{skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }  
Programming \& Python, PyTorch, TensorFlow, C/C++, Verilog, LATEX, MATLAB, Chisel, Arduino \\    
Language \& Mandarin Chinese (native speaker), English\\      
 
\end{tabular}   

\end{rSection}

\end{document}
